Embedded Scalars, Preferred Readings \& Intonation: {A}n Experimental Revisit

### 2014-05-29 text/paper/paper4.tex
K2 almost final

A number of empirical studies have already studied sentences like
(\ref{bsp:AE}) and (\ref{bsp:GE}) this issue
\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. Unfortunately,
results from these studies do not provide uncontroversial evidence to
decide between the two main rivaling positions. This is due to several
reasons. Firstly, previous studies have only accumulated limited
evidence pertaining to the preference relations between putative
readings of both types of sentences. Secondly, as
\citet{Tielvan-Tiel2012:Embedded-Scalar} and
\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue, the putative
evidence for the availability of local readings of \as-sentences
suggested by studies of \citet{CliftonDube2010:Embedded-Implic} and
\citet{ChemlaSpector2010:Experimental-Ev}, might well be confounds
with what van Tiel and Geurts call \emph{typicality effects}. Finally,
and most importantly, previous studies presented target sentences
visually. This is highly problematic, because traditionalists admit to
the availability of local readings as long as it is intonationally
marked
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}. We
will address this extant position as the \emph{intonational markedness
  hypothesis}. But if intonation plays a role, it is vital to present
target sentences auditorily, so as to be able to control for effects
of ``silent prosody'' that subjects may apply when reading a sentence
\citep[see][]{Bader98,Fodor98}.

@@

The data obtained by this method is problematic for both
traditionalism and grammaticalism. Contrary to the predictions of
traditionalism, we observed many answers indicative of local readings
of \es-sentences, irrespective of intonational markedness. But also
grammaticalism is incongruent with the observed pattern in our
data. Backed up by the Strongest Meaning Hypothesis
\citep{DalrympleKanazawa1998:Reciprocal-Expr}, grammaticalism predicts
local readings to be the preferred readings, but we found no evidence
for that. More strongly even, the preference order among putative
readings suggested by our data cannot even in principle be explained
by comparisons of logical strength among putative readings. In sum,
our data sheds doubt on both traditionalism and grammaticalism in
their currently most common forms. We conclude the paper by some
speculation about how either position might be amended in the light of
our data.

@@

\paragraph{Summary \& Interpretation.} High scores of success in
control conditions show that participants understood the incremental
verification task and were able to give judgements at the right point
in a picture sequence. Results for the preference-related controls
show that our design is able to detect multiple readings and
preferences among these. Crucially, the amount of response types for
\lc- and \ec-readings reflected the known preference for the former,
\emph{irrespective} of the order in which each reading could first be
judged in a given sequence. Finally, the incremental verification task
was generally sensitive to prosody. However, significant prosodic
effects were restricted to preference-related controls. Contrastively
accenting scalar \emph{some} generally led to more local readings, but
that effect was not significant. Local readings occurred in
\es-sentences, independently of prosody, but required intonational
marking in \as-sentences. Our analyses support the impression that
inspection of the raw data gives, namely that the general qualitative
pattern of reading preferences is the same for \as- and \es
conditions, namely that literal readings are preferred over local
readings which are preferred over global readings. More concretely,
our analyses suggest the following preference/availability patterns
(bracketed readings are unattested, in the sense that they are either
unavailable or heavily dispreferred):

@@

If we compare (\ref{bsp:observed-preferences}) with
Table~\ref{tab:predictions}, we quickly see that these findings are
not predicted by neither traditionalism nor
grammaticalism. Traditionalism, if left on its own, fails to predict
local readings in the \es-conditions. A Grammaticalism that relies on
the strongest meaning hypothesis fails to predict the right preference
order and cannot explain the absence of answers indicative of global
readings. Let's look more closely at what is and is not surprising
under each theoretical position and then reflect on how each position
might be adapted do deal with the observations that it does not
predict.

Traditionalism easily explains the absence of global readings. Weak
traditionalism, introduced in Section~\ref{sec:traditionalism}, for
instance, would hold that the extra assumptions needed to derive
global readings are not available or only allow for epistemic weak
implicatures that would be show as responses indicative of literal
readings in our task. In support of this view, traditionalists could
argue that the task's rather high processing demands lead to a
suppression of global readings, in line with the findings of
\citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
load negatively affects the number of scalar implicature responses in
sentence verification tasks. The small number of local readings in
\as-sentences with contrastive stress is easily explained by adopting
the Intonational Markedness Hypothesis. What traditionalism does not
predict is the high number of answers indicative of local readings in
the \es-conditions. Resorting to the Intonational Markedness
Hypothesis does not help, because local readings were observed for
accented as well as in unaccented \es-sentences. It would also remain
unclear why intonational cues should have such differential effects on
\as- and \es-sentences.

Grammaticalism, on the other hand, fails to predict the pattern in
(\ref{bsp:observed-preferences}) entirely if it equates preference for
readings with logical strength. Failure to predict the patter in
(\ref{bsp:observed-preferences}) is still relatively unproblematic for
\es-sentences, where strong grammaticalism (see
Section~\ref{sec:grammaticalism}) would simply not make any
predictions. But for \as-sentences grammaticalism would actually
predict that literal readings should be the least preferred. Again,
we need to bare the caveat of Section~\ref{sec:grammaticalism} in mind
that we are only evaluating grammaticalism with respect to a
particular selection criterion here. The verdict, however, seems to be
totally clear. If (\ref{bsp:observed-preferences}) is the actual
preference order over readings, then meaning selection in terms of
logical strength is generally on the wrong track, because no account
that merely looks at the logical strengths of readings can plausibly
predict the preference pattern in (\ref{bsp:observed-preferences}) for
both \as- and \es-sentences at the same time.

In sum, if we are justified in asserting that the pattern in
(\ref{bsp:observed-preferences}) reflects the true default preferences
over candidate readings (see below for a critical discussion), then
this cannot be explained in terms of the austere and stylized versions
of traditionalism and grammaticalism that we have set up so far. We
should then ask what plausible additional assumptions would enable
either framework accommodate the data? Again, let us look at each
position in turn.

Consider grammaticalism first. Our data quite clearly contradicts the
notion that preferences follow logical strength. It seems clear that
grammaticalism needs to be supplemented by a conceptually different
selection criterion. Selecting readings in terms of how well they
answer the contextually given question under discussion, as suggested
by \citet{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An},
is an option. But it is quite unclear what the question under
discussion should be that guided judgements in our task. As long as a
theory of accommodating implicit questions under discussion is
missing, this selection criterion does not make any clear, testable
predictions. However, looking at the qualitative pattern in
(\ref{bsp:observed-preferences}), a \emph{prima facie} plausible
disambiguation criterion is ready at hand: if we assume that each
insertion of the $\exh(\cdot)$ operator is \emph{costly}
anti-proportional to the depth of its embedding under other logical
operators, then we derive a preference of literal readings over local
ones over global ones. Whether such an \emph{economy principle} is
sound and in line with further empirical data would then be an
interesting matter of further investigation. What this economy
principle does not explain yet is the quantitative differences in the
preference orders between \as- and \es-sentences. Still, if combined
with further information about the global properties of the sentences
in question, this might be an interesting alternative disambiguation
criterion for an empirically testable grammaticalism.

Traditionalism, on the other hand, has to explain the possibility of
local readings of intonationally unmarked \es-sentences, and, perhaps,
also the large number of local readings in accented \es-sentence
compared to that in accented \as-sentences. To do so within a
traditionalist framework seems impossible, so the most common approach
is to explain putative evidence for local readings away as the result
of some other phenomenon, such as typicality or contrast
\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi,Tielvan-Tiel2014:Quantity-Matter}.
Since this ties into a critical reflection on our design, we will
enlarge on the possibility of typicality- and contrast-based effects
in our setting. Eventually, we argue that contrast-effects alone are
unlikely to explain the observed high number of local answers in
\es-sentences, but that the additional assumption of 
``shallow interpretation'' of the non-monotonic quantifiers might save
traditionalism.

@@

A more promising alternative explanation for local readings of
\es-sentences is pursued by
\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} \citep[see
also][]{Tielvan-Tiel2014:Quantity-Matter} in response to the data
reported by \citet{ChemlaSpector2010:Experimental-Ev}. The main idea
is that visual contrast between an item that is connected to all, and
one that is connected to only some but not all of the relevant
elements may trigger exceptional local enrichment of \emph{some}. In
support of this idea,
\citeauthor{GeurtsTielvan-Tiel2013:Scalar-expressi} show that the
strength of agreement to an \es-sentence on a 7-point Likert-scale
depends on how strong the relevant visual contrast is. When an item
with only some connections is contrasted presented alongside two
universally connected elements, the mean rate of agreement with a
suitable \es-sentence is significantly higher than when only one
universally connected element is present. So, maybe our \es-sequences
similarly provoked local readings because of an overemphasized visual
contrast between \emph{some but not all} and \emph{all}.

@@

What might make this contrast-based explanation more plausible is the
observation that subjects found \es-sentences difficult. As discussed
in Section~\ref{sec:results}, there were a non-negligible number of
\emph{true} answer at step 2 in the \es-sequence. This can be
explained on the assumption that participants read the non-monotonic
quantifier \emph{exactly one} as a monotonic quantifier \emph{at least
  one}. Similar ``shallow interpretation'' of \emph{exactly one} would
explain the high number of local answers for \es-sentences (and for
\es-sentence alone). If participants processed the truth-value for an
\es-sentence by looking for a \emph{unique} element that could be
singled out somehow, they would need to unravel the \es-sequence up to
the last picture. At this step contrast effects are stronger and would
not need to compete with the proper semantic interpretation of
\emph{exactly one}. Together, pictorial contrast effects in symbiosis
with a ``shallow interpretation'' non-monotonic quantifiers could be
an alternative explanation of (\ref{bsp:observed-preferences}) for
traditionalism.

@@

To begin with, it could be questioned whether our design reliably
indicates the preference relation in (\ref{bsp:observed-preferences})
among readings of our target sentences. After all, our incremental
verification task might simply select for the weakest possible
reading. This idea can be grounded in the observation that the
preferred \lc-readings of our target-related controls entail the
dispreferred \ec-readings. It could thus be argued that the difference
in responses for preference-related controls are due to the entailment
properties, not the known preference relation over \lc- and
\ec-readings. However, this does not explain why the distribution of
responses in the target conditions are obviously not governed by
logical strength. In fact, it is a very noteworthy point that although
entailment relations among readings differ between \as- and
\es-sentences, the observed response pattern does not. (This is what
is at the heart of the problem for a grammaticalism that relies on the
strongest meaning hypothesis.)

A related objection is that it is not feasible to actually compare
results from the preference-related controls to results from our
target conditions, because the source of different readings is
fundamentally different. In the former we have a syntactic ambiguity,
in the latter a set of putative pragmatic enrichments. The former is a
case of perceived ambiguity (some of our subjects reported this), the
latter arguably is not
\citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
if the distribution of responses is indicative of the known preference
patterns in preference-related controls, this would not necessarily
mean that the distribution of responses in target conditions is
indicative of preference relations. Although we cannot rule out that
the incremental verification task detects preferences among multiple
readings only for some sources of variability in readings and not
others, it is by no means clear why this should be so. The burden of
argument is on the sceptic. But even if we assume that the incremental
verification task is incapable of reliably indicating preferences
among candidate pragmatic enrichments of the relevant kind, then it
should at least be able to indicate availability of readings. So if we
deny the observed response patterns the power to indicate preference,
what should the information about availability of readings be that we
may safely infer from it? It should be that local readings are
available in \es-sentences and that global readings are unattested in
\as- and \es-sentences. But that alone is not predicted by either
traditionalism or grammaticalism. The former cannot explain the
substantial number of local responses in \es-sentences, the latter
does not explain the absence of total global responses.

Another line of criticism that challenges the validity of
(\ref{bsp:observed-preferences}) targets the Bayesian
salience-competition model that we used to derive it. We readily admit
that our model is highly simplistic. Several aspects are especially
noteworthy here. Firstly, we did not distinguish different types of
errors, and did not take into account that when errors occurred
earlier in the sequence, later decision points could no longer be
reached. This way the model may actually have unduly de-emphasized the
salience of readings that can be judged later in a sequence. Another,
more complicated model of the likelihood of answer patterns, might
therefore have given support to different conclusions. Unfortunately,
it is not clear how exactly such a more complex generating model
should be set-up. Eventually, a full processing model, design for data
from incremental verification tasks would be needed. We cannot offer
such a model here, but can only the offer the model that we did use as
a first step in that direction. More importantly, though, the only
part of our conclusions that might plausibly change in
(\ref{bsp:observed-preferences}) for a different generating model is
that the 3 \emph{false} answers in the \as-conditions with neutral
intonation might support the conclusion that the local reading is
marginally attested. But this hypothetical effect will certainly be no
bigger than marginal, and so no genuinely different conclusions of
theoretical relevance should be expected.

@@

We tested experimentally the predictions of traditionalism and
grammaticalism with respect to the availability of and preferences
over three types of conceivable pragmatic enrichments of two types of
sentences, in which scalar \emph{some} occurred in the scope of either
a monotonic quantifier \emph{all} or the non-monotonic quantifier
\emph{exactly one}. To avoid potential confounds of the pictorial
material, such as through typicality or contrast
\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi},
we employed an incremental verification task \citep{Conroy2008}, in
which subjects were presented with partially covered pictures and
asked to uncover the picture sequentially until they felt able to give
a categorical truth-value judgements. In order to control for
potential confounds of ``silent prosody,'' sentence material was
presented auditorily and contrastive stress on embedded \emph{some}
was manipulated. This way we were able to also explicitly test the
intonational markedness hypothesis, which is often used to supplement
traditionalism. Additionally, we included preference-related control
conditions in order to be able to deduce latent preferences for
candidate readings from the answer patterns we gathered. To this end,
we introduced a generative Bayesian model that gives probabilistic
predictions about possibly observable answer patterns in our task,
given concrete instances of relatives saliences of readings and other
parameters. Using the observed data, in particular in connection with
the preference-related control conditions, we inferred a posteriori
likely values of the latent cognitive parameters.

>>>>

A number of empirical studies have already studied sentences like
(\ref{bsp:AE}) and (\ref{bsp:GE})
\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. Unfortunately,
results from these studies do not provide uncontroversial
evidence. This is due to several reasons. Firstly, previous studies
have only accumulated limited evidence pertaining to the preference
relations between candidate readings of both types of
sentences. Secondly, as \citet{Tielvan-Tiel2012:Embedded-Scalar} and
\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} argue, the alleged
evidence for the availability of local readings of \as-sentences
suggested by studies of \citet{CliftonDube2010:Embedded-Implic} and
\citet{ChemlaSpector2010:Experimental-Ev}, might well be confounds
with what van Tiel and Geurts call \emph{typicality effects}. Finally,
and most importantly, previous studies presented target sentences
visually. This is highly problematic, because traditionalists admit to
the availability of local readings as long as it is intonationally
marked
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi}. We
will address this extant position as the \emph{intonational markedness
  hypothesis}. But if intonation plays a role, it is vital to present
target sentences auditorily, so as to be able to control for effects
of ``silent prosody'' that subjects may apply when reading a sentence
\citep[see][]{Bader98,Fodor98}.

@@

The data obtained by this method is problematic for both
traditionalism and grammaticalism. Contrary to the predictions of
traditionalism, we observed many answers indicative of local readings
of \es-sentences, irrespective of intonational markedness. But also
grammaticalism is incongruent with the observed pattern in our
data. Backed up by the strongest meaning hypothesis
\citep{DalrympleKanazawa1998:Reciprocal-Expr}, grammaticalism predicts
local readings to be the preferred readings, but we found no evidence
for that. More strongly even, the preference order among putative
readings suggested by our data cannot even in principle be explained
by comparisons of logical strength among putative readings. In sum,
our data sheds doubt on both traditionalism and grammaticalism in
their currently most common forms. We conclude the paper by some
speculation about how either position might be amended in the light of
our data.

@@

\paragraph{Summary \& Interpretation.} High scores of success in
control conditions show that participants understood the incremental
verification task and were able to give judgements at the right point
in a picture sequence. Results for the preference-related controls
show that our design is able to detect multiple readings and
preferences among these. Crucially, the amount of response types for
\lc- and \ec-readings reflected the known preference for the former,
with a mild bias for readings that can be judged later in the
sequence. Also, the incremental verification task was generally
sensitive to prosody. However, significant prosodic effects were
restricted to preference-related controls. Contrastively accenting
scalar \emph{some} generally led to more local readings, but that
effect was not significant. Local readings occurred in \es-sentences,
independently of prosody, but required intonational marking in
\as-sentences. Our analyses support the impression that inspection of
the raw data gives, namely that the general qualitative pattern of
reading preferences is the same for \as- and \es-conditions: literal
readings are preferred over local readings which are preferred over
global readings. More concretely, our analyses suggest the following
preference/availability patterns (bracketed readings are unattested,
in the sense that they are either unavailable or heavily
dispreferred):

@@

If we compare (\ref{bsp:observed-preferences}) with
Table~\ref{tab:predictions}, we quickly see that these findings are
not predicted by either traditionalism or
grammaticalism. Traditionalism fails to predict local readings in the
\es-conditions. Disambiguation in terms of logical strength has
grammaticalism mispredict the observed reading preferences. Let's look
more closely at what is and is not surprising under each theoretical
position and then reflect on how each position might be adapted do
deal with the observations that it does not predict.

Traditionalism easily explains the absence of global readings. Weak
traditionalism, introduced in Section~\ref{sec:traditionalism}, for
instance, would hold that the extra assumptions needed to derive
global readings are not available or only allow for epistemic weak
implicatures that would show as responses indicative of literal
readings in our task. In support of this view, traditionalists could
argue that the task's rather high processing demands lead to a
suppression of global readings, in line with the findings of
\citet{NeysDe-NeysSchaeken2007:When-People-Are} that working memory
load negatively affects the number of scalar implicature responses in
sentence verification tasks. The small number of local readings in
\as-sentences with contrastive stress is easily explained by adopting
the intonational markedness hypothesis. What traditionalism does not
predict is the high number of answers indicative of local readings in
the \es-conditions. Resorting to the intonational markedness
hypothesis does not help, because local readings were observed for
accented as well as in unaccented \es-sentences. It would also remain
unclear why intonational cues should have such differential effects on
\as- and \es-sentences.

Grammaticalism, on the other hand, fails to predict the pattern in
(\ref{bsp:observed-preferences}) entirely if it equates preference for
readings with logical strength. Grammaticalism predicts that literal
readings of \as-sentences are the least preferred, contrary to
(\ref{bsp:observed-preferences}). Again, we need to bare the caveat of
Section~\ref{sec:grammaticalism} in mind that we are only evaluating
grammaticalism with respect to a particular selection criterion
here. The verdict, however, seems to be clear. If
(\ref{bsp:observed-preferences}) is the actual preference order over
readings, then meaning selection in terms of logical strength is
generally on the wrong track, because no account that merely looks at
the logical strengths of readings can plausibly predict the preference
pattern in (\ref{bsp:observed-preferences}) for both \as- and
\es-sentences at the same time.

In sum, if we are justified in asserting that the pattern in
(\ref{bsp:observed-preferences}) reflects the true default preferences
over candidate readings (see below for a critical discussion), then
this cannot be explained in terms of the austere and stylized versions
of traditionalism and grammaticalism that we have set up so far. We
should then ask what plausible additional assumptions would enable
either framework to accommodate the data? Again, let us look at each
position in turn.

Consider grammaticalism first. Our data quite clearly contradicts the
notion that preferences follow logical strength. But grammaticalism
could be supplemented by a conceptually different selection
criterion. Selecting readings in terms of how well they answer the
contextually given question under discussion, as suggested by
\citet{Fox2007:Free-Choice-and,GualminiHulsey2008:The-Question-An}, is
an option. But it is quite unclear what the question under discussion
should be that guided judgements in our task. As long as a theory of
accommodating implicit questions under discussion is missing, this
selection criterion does not make any clear, testable
predictions. However, looking at the qualitative pattern in
(\ref{bsp:observed-preferences}), a \emph{prima facie} plausible
disambiguation criterion is ready at hand: if we assume that each
insertion of the $\exh(\cdot)$ operator is \emph{costly}
anti-proportional to the depth of its embedding under other logical
operators, then we derive a preference of literal readings over local
ones over global ones. Whether such an \emph{economy principle} is
sound and in line with further empirical data would then be an
interesting matter of further investigation. What this economy
principle does not explain yet is the quantitative differences in the
preference orders between \as- and \es-sentences. Still, if combined
with further information about the global properties of the sentences
in question, this might be an interesting alternative disambiguation
criterion for an empirically testable grammaticalism.

Traditionalism, on the other hand, has to explain the possibility of
local readings of intonationally unmarked \es-sentences, and, perhaps,
also the large number of local readings in accented \es-sentences
compared to that in accented \as-sentences. To do so within a
traditionalist framework is difficult, if possible at all. A common
approach is to explain putative evidence for local readings away as
the result of some other phenomenon, such as typicality or contrast
\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi,Tielvan-Tiel2014:Quantity-Matter}.
Since this ties into a critical reflection on our design, we will
enlarge on the possibility of typicality- and contrast-based effects
in our setting. Eventually, we argue that contrast-effects alone are
unlikely to explain the observed high number of local answers in
\es-sentences, but that the additional assumption of ``shallow
interpretation'' of the non-monotonic quantifiers might save
traditionalism.

@@

A more promising alternative explanation for local readings of
\es-sentences is pursued by
\citet{GeurtsTielvan-Tiel2013:Scalar-expressi} in response to the data
reported by \citet{ChemlaSpector2010:Experimental-Ev}. The main idea
is that visual contrast between an item that is connected to all, and
one that is connected to only some but not all of the relevant
elements may trigger exceptional local enrichment of \emph{some}. In
support of this idea,
\citeauthor{GeurtsTielvan-Tiel2013:Scalar-expressi} show that the
strength of agreement to an \es-sentence on a 7-point Likert-scale
depends on how strong the relevant visual contrast is. When an item
with only some connections is presented alongside two universally
connected elements, the mean rate of agreement with a suitable
\es-sentence is significantly higher than when only one universally
connected element is present. So, maybe our \es-sequences similarly
provoked local readings because of an overemphasized visual contrast
between \emph{some but not all} and \emph{all}.

@@

On the other hand, what might make this contrast-based explanation
more plausible is the observation that subjects found \es-sentences
difficult. As discussed in Section~\ref{sec:results}, there were a
non-negligible number of \emph{true} answer at step 2 in the
\es-sequence. This can be explained on the assumption that
participants read the non-monotonic quantifier \emph{exactly one} as a
monotonic quantifier \emph{at least one}. Similar ``shallow
interpretation'' of \emph{exactly one} would explain the high number
of local answers for \es-sentences (and for \es-sentence alone). If
participants processed the truth-value for an \es-sentence by looking
for a \emph{unique} element that could be singled out a description
like ``\dots is connected to some of its \dots'', they would need to
unravel the \es-sequence up to the last picture where the relevant
visual contrast is stronger. A ``shallow interpretation''-theory also
sidesteps the puzzle why answers are given that are incompatible with
the proper semantic meaning of \es-sentences. Together, pictorial
contrast effects in symbiosis with a ``shallow interpretation'' of
non-monotonic quantifiers could be an alternative explanation of
(\ref{bsp:observed-preferences}) for traditionalism.

@@

To begin with, it could be questioned whether our design reliably
indicates the preference relations in
(\ref{bsp:observed-preferences}). One could object that it is not
feasible to compare results from the preference-related controls to
results from our target conditions, because the source of different
readings is fundamentally different. In the former we have a syntactic
ambiguity, in the latter a set of putative pragmatic enrichments. The
former is a case of perceived ambiguity (some of our subjects reported
this), the latter arguably is not
\citep[see][]{GeurtsPouscoulous2009:Embedded-Implic}. So perhaps even
if the distribution of responses is indicative of the known preference
patterns in preference-related controls, this would not necessarily
mean that the distribution of responses in target conditions is
indicative of preference relations. Although we cannot rule out that
the incremental verification task detects preferences among multiple
readings only for some sources of variability in readings and not
others, it is by no means clear why this should be so. The burden of
argument is on the sceptic. But even if we assume that the incremental
verification task is incapable of reliably indicating preferences
among candidate pragmatic enrichments of the relevant kind, then it
should at least be able to indicate availability of readings. So if we
deny the observed response patterns the power to indicate preference,
what should the information about availability of readings be that we
may safely infer from it? It should be that local readings are
available in \es-sentences and that global readings are unattested in
\as- and \es-sentences. But that alone is not predicted by either
traditionalism or grammaticalism. The former cannot explain the
substantial number of local responses in \es-sentences, the latter
does not explain the absence of total global responses.

Another line of criticism that challenges the validity of
(\ref{bsp:observed-preferences}) targets the Bayesian
salience-competition model that we used to derive it. We readily admit
that our model is highly simplistic. Several aspects are especially
noteworthy here. Firstly, we did not distinguish different types of
errors, and did not take into account that when errors occurred
earlier in the sequence, later decision points could no longer be
reached. This way the model may actually have unduly de-emphasized the
salience of readings that can be judged later in a sequence. Another,
more complicated model of the likelihood of answer patterns, might
therefore have given support to different conclusions. Unfortunately,
it is not clear how exactly such a more complex generating model
should be set-up. Eventually, a full processing model, designed for
data from incremental verification tasks, would be needed. We cannot
offer such a model here, but can only the offer a first step in that
direction. More importantly, though, the only part of
(\ref{bsp:observed-preferences}) that might plausibly change for a
more encompassing model along the lines sketched above is that the 3
\emph{false} answers in the \as-conditions with neutral intonation
might support the conclusion that the local reading is attested. But
this hypothetical effect will certainly be no bigger than marginal,
and so no genuinely different conclusions of theoretical relevance
should be expected.

@@

We tested experimentally the predictions of traditionalism and
grammaticalism with respect to the availability of and preferences
over three types of conceivable pragmatic enrichments of two types of
sentences, in which scalar \emph{some} occurred in the scope of either
a monotonic quantifier \emph{all} or the non-monotonic quantifier
\emph{exactly one}. To avoid potential confounds of the pictorial
material, such as through typicality or contrast
\citep{Tielvan-Tiel2012:Embedded-Scalar,GeurtsTielvan-Tiel2013:Scalar-expressi},
we employed an incremental verification task \citep{Conroy2008}, in
which subjects were presented with partially covered pictures and
asked to uncover the picture sequentially until they felt able to give
a categorical truth-value judgements. In order to control for
potential confounds of ``silent prosody,'' sentence material was
presented auditorily and contrastive stress on embedded \emph{some}
was manipulated. This way we were able to also explicitly test the
intonational markedness hypothesis, which is often used to supplement
traditionalism. Additionally, we included preference-related control
conditions in order to be able to deduce latent preferences for
candidate readings from the answer patterns we gathered. To this end,
we introduced a generative Bayesian model that gives probabilistic
predictions about observable answer patterns in our task, given
concrete instances of relative saliences of readings and other
parameters. Using the observed data, in particular in connection with
the preference-related control conditions, we inferred a posteriori
likely values of the latent cognitive parameters.
